Faithful Variable Screening for\\ High-Dimensional Convex Regression

### 2014-11-25 tex/scam/appendix.tex
mods for aos submission

Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n > | \frac{1}{2n}
\hat{r}^\tran \mathbf{1}_{(i:n)}|$ where $\mathbf{1}_{(i:n)}$ is 1 on the coordinates of the $i$-th largest to the $n$-th largest entries of $X_k$ and 0 elsewhere.
Then the following are true:
\begin{enumerate}
\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be zero and must be unique.
\end{enumerate}
\end{theorem}

\begin{proof} 
We will omit the Lipschitz constraint in our proof here. It can be
added in and easily verified that the result of the theorem still holds.

@@

We now verify that stationarity holds also for $k \in S^c$. We fix one dimension $k \in S^c$ and let $\hat{r} = Y - \sum_{k' \in S} \bar{\Delta}_{k'} \hat{d}_{k'}$. 
The Lagrangian form of the optimization, in terms of just $d_k$, is
\[
\mathcal{L}(d_k, \nu_k) =
  \frac{1}{2n} \big\| Y - \sum_{k' \in S} \bar{\Delta}_{k'} d_{k'} 
  -  \bar{\Delta}_k d_k \big\|_2^2 
   + \lambda \| \bar{\Delta}_k d_k\|_\infty
  - \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
\]
with the constraint that $v_i \geq 0$ for all $i$.

The derivative of the Lagrangian is
\begin{align*}
\partial_{d_k} \mathcal{L}(d_k) =  -\frac{1}{n} \bar{\Delta}_k^\tran ( Y - \sum_{k'\in S} \bar{\Delta}_{k'} d_{k'}  - \bar{\Delta}_k d_k )
        + \lambda \bar{\Delta}_k^\tran \mathbf{u}
      - \nu_k
\end{align*}
where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$, an $n$-vector such that $\| \mathbf{u}_T \|_1 = 1$ where $T = \{ i \,:\,  (\bar{\Delta}_k d_k)_i = \| \bar{\Delta}_k d_k \|_\infty \}$.

We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the duals can be set in a way to ensure that the derivatives are equal to zero,
\begin{align*}
\partial_{d_k} \mathcal{L}(\hat{d}_k) = -\frac{1}{n} \bar{\Delta}_k^\tran\hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}
           - \nu_k = 0 
\end{align*}
where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$. It clear that to show stationarity, we only need to show that $-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} \geq 0$ where the inequality is element-wise.

Let us reorder the samples so that the $i$-th sample is the $i$-th smallest sample. 
We will construct $\gamma = 0$, and $\mathbf{u} = (-a, 0, ..., a)$ for
some $0 < a < 1/2$, where the coordinates of $\mathbf{u}$ correspond
to the new sample ordering. 
We then just need to show that
\begin{align*}
- \frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow \\
- \frac{1}{n} \Delta_k^\tran \hat{r} + \lambda \Delta_k^\tran \mathbf{u} &\geq 0 \quad \Leftrightarrow\\
- \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad 
   \textrm{for each } j \\
- \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i 
    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i 
    + \lambda (X_{kn} - X_{kj})a &\geq 0 \\
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{(i':n)}^\tran \hat{r} 
   + \lambda (X_{kn} - X_{kj})a &\geq 0 
\end{align*}
where $\mathsf{gap}_i = X_{ki} - X_{k,i-1}$. If $\frac{1}{2n} |\mathbf{1}_{(i:n)}^\tran \hat{r}| \leq \lambda a$ for all $i=1,...,n$, then we have that
\begin{align*}
- \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}
   + \lambda (X_{kn} - X_{kj})a &\geq 0 \quad \Leftrightarrow \\
- \sum_{i' > j} \mathsf{gap}_{i'} \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0\\
- (X_{kn} - X_{kj}) \lambda a + \lambda (X_{kn} - X_{kj}) a &\geq 0.
\end{align*}
We have thus proven that there exists one solution $\{ \hat{d}_k
\}_{k=1,...,p}$ such that $\hat{d}_k = 0$ for all $k \in
S^c$. Furthermore, we have shown that the subgradient variables
$\mathbf{u}_k$ of the solution $\{ \hat{d}_k \}$ can be chosen such
that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$.

@@

\begin{theorem} 
Suppose assumptions A1-A4 hold. Suppose $\sqrt{\log 2np} \geq 1$, and define $\tilde{\sigma} \equiv \max(\sigma, B)$.

If $\lambda_n \geq 8 s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{12}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
\[
\lambda_n > \Big| \frac{1}{2n}\hat{r}^\tran \mathbf{1}_{(i':n)_k} \Big|.
\]
Therefore, for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$ from optimization~\ref{opt:alternate_opt_concave} are zero. 
\end{theorem}

@@

Fix $j$ and $i$. Then $\hat{r}^\tran \mathbf{1}_{(i':n)_k}$ is the sum
of $n-i'+1$ random coordinates of $\hat{r}$. We will use
Serfling's theorem on the concentration of measure of sampling without
replacement (Corollary~\ref{cor:serfling}). We must first bound $\|
\hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we
can use Serfling's results however.

\vskip5pt
\textbf{Step 1}: {\it Bounding $\| \hat{r} \|_\infty$.} We have $\hat{r}_i = f_0(x_i) + w_i - \hat{f}(x_i)$ where
$\hat{f}(x_i) = \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ is the convex
additive function outputted by the restricted regression. Note that
both $f_0(x_i)$ and $\hat{f}(x_i)$ are bounded by $sB$. 
Because $w_i$ is sub-Gaussian, $|w_i| \leq  \sigma \sqrt{2\log \frac{2}{\delta}}$ with probability at most $1-\delta$. By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \sigma \sqrt{ 2 \log \frac{2n}{\delta}}$ with probability at most $1 - \delta$.

Putting these observations together,
%and take another union bound across all $j$ and all $i'$:
\begin{align}
\| \hat{r} \|_\infty &\leq 2sB + \sigma \sqrt{ 2\log \frac{2n}{\delta}}) \nonumber \\
      &\leq 4 s \tilde{\sigma} \sqrt{\log \frac{2n}{\delta}} \label{eqn:stepone_rhat}
\end{align}
with probability at least $1 - \delta$, where we have defined
$\tilde{\sigma} = \max(\sigma, B)$,
and assumed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$, which is acceptable since $\delta \leq 1$ and the theorem presupposes that $\sqrt{ \log 2np } \geq 1$.

@@

\vskip5pt
\textbf{Step 3}: {\it Apply Serfling's theorem.}  
For any $k \in S^c$, Serfling's theorem states that with probability at least $1 - \delta$
\begin{align*}
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)_k}\Big| \leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{2}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|
\end{align*}
We need Serfling's theorem to hold for all $k = 1,...,p$ and $i' =
1,...,n$. We also need the events that $\|\hat{r}\|_\infty$ and $|
\frac{1}{n} \hat{r}^\tran \mathbf{1}|$ are small to hold. Using a
union bound, with probability at least $1-\delta$, for all $k,i'$,
\begin{align*}
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{(i':n)_k}\Big| &\leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{6np}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|\\
  &\leq 4s\tilde{\sigma}\sqrt{\log \frac{6n}{\delta}} \sqrt{\frac{1}{n}\log \frac{6np}{\delta}} + 4 s \tilde{\sigma} \sqrt{\frac{1}{n}\log \frac{12}{\delta}} \\
  &\leq 8 s\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 \frac{12np}{\delta}}
\end{align*}
In the second inequality, we used equation~\eqref{eqn:stepone_rhat}
and equation~\eqref{eqn:steptwo_rhat} from steps 1 and 2
respectively. Setting $\delta = \frac{12}{n}$ gives the desired
result.
\end{proof}

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
minimizer of the restricted regression with $\lambda \leq 9 s
\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
Suppose $n \geq c_1 \max(\sqrt{sB}, B)$.
Then with probability at least $1-\frac{C}{n}$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np},
\end{align}
where $c, C$ are constants, possibly dependent on $c_1, b$.
\end{theorem}

@@

\begin{theorem}
\label{thm:concave_consistent}
Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
step with $\lambda_n \leq 9 sB \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq B^4 \tilde{\sigma}^2 s^5$.
Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
\[
\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \sigma^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
\]
\end{theorem}

>>>>

Let $\pi_k(i)$ be an reordering of $X_k$ in ascending order so that $X_{k \pi_k(n)}$ is the largest entry. Let $\mathbf{1}_{\pi_k(i:n)}$ be 1 on the coordinates $\pi_k(i),\pi_k(i+1),...,\pi_k(n)$ and 0 elsewhere. Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k \pi_k(1)}$.

Suppose for all $k\in S^c$ and for all $i=1,...,n$, $\lambda_n \geq \mathsf{range}_k | \frac{32}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i:n)}|$, and $\max_{i=1,...,n-1} \frac{X_{k\pi_k(i+1)} - X_{k\pi_k(i)}}{\mathsf{range}_k} \geq \frac{1}{16}$, and $\mathsf{range}_k \geq 1$.

Then the following are true:
\begin{enumerate}
\item Let $\hat{d}_k = 0$ for $k \in S^c$, then \{$\hat{d}_k\}_{k=1,...,p}$ is an optimal solution to optimization~\ref{opt:alternate_opt}. Furthermore, any solution to the optimization program \ref{opt:alternate_opt} must be zero on $S^c$.
\item For all $k \in S^c$, the solution to optimization~\ref{opt:alternate_opt_concave} must be zero and unique.
\end{enumerate}
\end{theorem}

\begin{proof} 
We will omit the $B$-boundedness constraint in our proof here. It is easy to verify that the result of the theorem still holds with the constraint added in.

@@

We now verify that stationarity holds also for $k \in S^c$. We fix one dimension $k \in S^c$ and let $\hat{r} = Y - \sum_{k' \in S} \bar{\Delta}_{k'} \hat{d}_{k'}$. 
The Lagrangian form of the optimization, in terms of just $d_k$, is
\[
\mathcal{L}(d_k, \nu_k) =
  \frac{1}{2n} \big\| Y - \sum_{k' \in S} \bar{\Delta}_{k'} d_{k'} 
  -  \bar{\Delta}_k d_k \big\|_2^2 
   + \lambda \| \bar{\Delta}_k d_k\|_\infty
  - \sum_{i=2}^{n-1} \nu_{ki} d_{ki}
\]
with the constraint that $v_{ki} \geq 0$ for $i=2,...,n-1$.

The derivative of the Lagrangian is
\begin{align*}
\partial_{d_k} \mathcal{L}(d_k) =  -\frac{1}{n} \bar{\Delta}_k^\tran ( Y - \sum_{k'\in S} \bar{\Delta}_{k'} d_{k'}  - \bar{\Delta}_k d_k )
        + \lambda \bar{\Delta}_k^\tran \mathbf{u}
      - \left( \begin{array}{c} 0 \\ \nu_k \end{array} \right)
\end{align*}
where $\mathbf{u}$ is the subgradient of $\| \bar{\Delta}_k d_k \|_\infty$. If $\bar{\Delta}_k d_k = 0$, then $\mathbf{u}$ can be any vector whose $L_1$ norm is less than or equal to $1$. $\nu_k \geq 0$ is a vector of Lagrangian multipliers. $\nu_{k1}$ does not exist because $d_{k1}$ is not constrained to be non-negative.

We now substitute in $d_{k'} = \hat{d}_{k'}$ for $k' \in S$, $d_k = 0$ for $k \in S$, and $r = \hat{r}$ and show that the $\mathbf{u}, \nu_k$ dual variables can be set in a way to ensure that stationarity:
\begin{align*}
\partial_{d_k} \mathcal{L}(\hat{d}_k) = -\frac{1}{n} \bar{\Delta}_k^\tran\hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}
           - \left( \begin{array}{c} 0 \\ \nu_k \end{array} \right) = 0 
\end{align*}
where $\| \mathbf{u} \| \leq 1$ and $\nu_k \geq 0$. It clear that to show stationarity, we only need to show that $[-\frac{1}{n} \bar{\Delta}_k^\tran \hat{r} + \lambda \bar{\Delta}_k^\tran \mathbf{u}]_j = 0$ for $j=1$ and $\geq 0$ for $j=2,...,n-1$.

To ease notational burden, let us reorder the samples in ascending order so that the $i$-th sample is the $i$-th smallest sample. We will from here on write $X_{ki}$ to denote $X_{k \pi_k(i)}$.

Define $i^*$ as the largest index such that $\frac{X_{kn} - X_{ki^*}}{X_{kn} - X_{k1}} \geq 1/2$. 
We will construct $\mathbf{u} = (a - a', 0, ..., -a, 0,..., a')$ where
$a,a'$ are positive scalars, where $-a$ lies at the $i^*$-th coordinate, and where the coordinates of $\mathbf{u}$ correspond
to the new sample ordering.

We define

\begin{align*}
\kappa &= \frac{1}{\lambda n} \big[ \Delta_k^\tran \hat{r} \big]_1 \\
a' &= \frac{X_{kn} - X_{k1}}{X_{kn} -  X_{ki^*}} \kappa + 
     \frac{X_{ki^*}-X_{k1}}{X_{kn} - X_{k i^*}} \frac{1}{8} \\
a &= \frac{X_{kn} - X_{k1}}{X_{kn} -  X_{ki^*}} \kappa + 
     \frac{X_{kn}-X_{k1}}{X_{kn} - X_{ki^*}} \frac{1}{8} \\
\end{align*}

and we verify two facts: first that the KKT stationarity is satisfied and second, that $\| \mathbf{u} \|_1 < 1$ with high probability. Our claim is proved immediately by combining these two facts.

Because $\hat{r}$ and $\mathbf{u}$ are both centered vectors, $\bar{\Delta}_k^\tran \hat{r} = \Delta_k^\tran \hat{r}$ and likewise for $\mathbf{u}$. Therefore, we need only show that for $j=1$, $\lambda \big[ \Delta_k^\tran \mathbf{u} \big]_j = \big[ \frac{1}{n} \Delta_k^\tran \hat{r} \big]_j$ and that for $j = 2,..., n-1$, $\lambda \big[ \Delta_k^\tran \mathbf{u} \big]_j \geq \big[ \frac{1}{n} \Delta_k^\tran \hat{r} \big]_j$.

With our explicitly defined form of $\mathbf{u}$, we can characterize
\begin{align}
\big[ \Delta_k^\tran \mathbf{u} \big]_j = 
  \left \{ \begin{array}{cc} 
   (-a + a')(X_{k i^*} - X_{kj})+ a'(X_{kn} - X_{k i^*})
   & \trm{ if } j \leq i^* \\
   a'(X_{kn} - X_{kj}) & \trm{ if } j \geq i^* 
     \end{array} \right.
\end{align}

It is straightforward to check that $\big[ \lambda \Delta_k^\tran \mathbf{u} \big]_1 = \lambda \kappa = \frac{1}{n} \big[ \Delta_k^\tran \hat{r} \big]_1$.

To check that other rows of stationarity condition holds, we characterize $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$:
\begin{align*}
[\frac{1}{n} \Delta_k^\tran \hat{r}]_j &= \frac{1}{n} \sum_{i > j} (X_{ki} - X_{kj}) \hat{r}_i \\
  & = \frac{1}{n} \sum_{i > j} \sum_{j < i' \leq i} \mathsf{gap}_{i'} \hat{r}_i \\
 & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \sum_{i \geq i'} \hat{r}_i \\
 & = \frac{1}{n} \sum_{i' > j} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r} 
\end{align*}
where we denote $\mathsf{gap}_{i'} = X_{ki'} - X_{k(i'-1)}$.

We pause for a second here to give a summary of our proof strategy. We leverage two critical observations: first, any two adjacent coordinates in the vector $\frac{1}{n} \Delta_k^\tran \hat{r}$ cannot differ by too much. Second, we defined $a, a'$ such that $-a+a' = -\frac{1}{8}$ so that $\lambda \Delta_k^\tran \mathbf{u}$ is a sequence that strictly increases in the first half (for coordinates in $\{1,...,i^*\}$) and strictly decreases in the second half.

We know $\frac{1}{n} \Delta_k^\tran \hat{r}$ and $\lambda \Delta_k^\tran \mathbf{u}$ are equal in the first coordinate. We will show that the second sequence increases faster than the first sequence which will imply that the second sequence is larger than the first in the first half of the coordinates. We will then work similarly but backwards for the second half.

Following our strategy, We first compare $[\lambda \Delta_k^\tran \mathbf{u}]_j$ and $[\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for $j=1,..., i^*-1$.

For $j = 1,..., i^*-1$, we have that
\begin{align*}
\lambda [ \Delta_k^\tran \mathbf{u}]_{j+1} - \lambda [ \Delta_k^\tran \mathbf{u}]_{j} &= \lambda (a - a') \mathsf{gap}_{j+1} \\
 &\geq -\mathsf{gap}_{j+1} \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r} \\
& = [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{j+1} - [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{j}
\end{align*}

The inequality follows because $a - a' = \frac{1}{8}$ and thus $\lambda (a - a') \geq \left| \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r} \right|$. Therefore, for all $j = 1,...,i^*$:
\begin{align*}
[ \lambda \Delta_k^\tran \mathbf{u}]_j &\geq [ \frac{1}{n} \Delta_k^\tran \hat{r} ]_j
\end{align*}

For $j \geq i^*$, we start our comparison from $j=n-1$. First, we claim that $a' > \frac{1}{32}$. To prove this claim, note that
\begin{align}
|\kappa| &= \Big|\frac{1}{\lambda n} \sum_{i' > 1} \mathsf{gap}_{i'} \mathbf{1}_{i':n}^\tran \hat{r}\Big| \leq \frac{1}{X_{kn} - X_{k1}}\frac{1}{32} \sum_{i' > 1} \mathsf{gap}_{i'} 
 = \frac{1}{32} 
\end{align}
and that
\begin{align*}
\frac{X_{kn} - X_{ki^*}}{X_{kn} - X_{k1}} &= \frac{X_{kn} - X_{k(i^*+1)} + X_{k(i^*+1)} - X_{ki^*}}{X_{kn} - X_{k1}} \leq \frac{1}{2} + \frac{1}{16}
\end{align*}
where the inequality follows because we had assumed that $\frac{X_{k(i+1)} - X_{ki}}{X_{k(n)} - X_{k(1)}} \leq \frac{1}{16}$ for all $i = 1,...,n-1$.

So, we have 
\begin{align*}
a' &= \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \kappa 
   + \frac{ X_{ki^*} - X_{k1}}{X_{kn} - X_{ki^*}} \frac{1}{8} \\
 &= \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \left(
  \kappa + \frac{X_{ki^*} - X_{k1}}{X_{kn} - X_{k1}} \frac{1}{8} \right) \\
&\geq \frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \left(
  -\frac{1}{32} + (\frac{1}{2} - \frac{1}{16}) \frac{1}{8} \right) \\
&\geq \frac{1}{1/2 + 1/16} \left(
  -\frac{1}{32} + (\frac{1}{2} - \frac{1}{16}) \frac{1}{8} \right) \\
&\geq \frac{1}{32}
\end{align*}
In the first inequality of the above derivation, we used the fact that $\frac{X_{ki^*} - X_{k1}}{X_{kn} - X_{k1}} \leq \frac{1}{2} - \frac{1}{16}$. In the second inequality, we used the fact that the quantity inside the parentheses is positive and $\frac{X_{kn} - X_{k1}}{X_{kn} - X_{ki^*}} \geq \frac{1}{1/2 + 1/16}$.

Now consider $j=n-1$. 
\[
[ \frac{1}{n} \Delta_k^\tran \hat{r} ]_{n-1} = \frac{1}{n} \mathsf{gap}_n \hat{r}_n 
 \leq \mathsf{gap}_n \frac{\lambda }{32} \leq \lambda \mathsf{gap}_n a' = \lambda [\Delta_k^\tran \mathbf{u}]_{n-1} 
\]

For $j = i^*, ..., n-2$, we have that 
\begin{align*}
\lambda [\Delta_k^\tran \mathbf{u} ]_j - \lambda [\Delta_k^\tran \mathbf{u}]_{j+1} &= 
 \lambda a' \mathsf{gap}_{j+1}  \\
 &\geq \mathsf{gap}_{j+1} \frac{1}{n} \mathbf{1}_{(j+1):n}^\tran \hat{r}  \\
 &\geq  [\frac{1}{n} \Delta_k^\tran \hat{r}]_j - [\frac{1}{n} \Delta_k^\tran \hat{r}]_{j+1}
\end{align*}

Therefore, for $j = i^*,...,n-2$,
\begin{align*}
\lambda [\Delta_k^\tran \mathbf{u}]_j \geq \frac{1}{n} [ \Delta_k^\tran \hat{r}]_j
\end{align*}

We conclude then that $\lambda [\Delta_k^\tran \mathbf{u} ]_j \geq [\frac{1}{n} \Delta_k^\tran \hat{r}]_j$ for all $j = 2,...,n-1$.

We have thus verified that the stationarity equations hold and now will bound $\| \mathbf{u} \|_1$.

\begin{align*}
\| \mathbf{u} \|_1 = | a - a'| + a + a' \leq \frac{1}{8} + 2 a \leq \frac{1}{8} + 4 |\kappa| + \frac{1}{2}  \leq \frac{1}{8} + \frac{1}{8} + \frac{1}{2} < 1
\end{align*}
In the third inequality, we used the fact that $|\kappa| \leq \frac{1}{32}$.

We have thus proven that there exists one solution $\{ \hat{d}_k
\}_{k=1,...,p}$ such that $\hat{d}_k = 0$ for all $k \in
S^c$. Furthermore, we have shown that the subgradient variables
$\mathbf{u}_k$ of the solution $\{ \hat{d}_k \}$ can be chosen such
that $\| \mathbf{u}_k \|_1 < 1$ for all $k \in S^c$.

@@

\begin{theorem} 
Suppose assumptions A1-A5 hold. Define $\tilde{\sigma} \equiv \max(\sigma, B)$. Suppose that $p \leq O\big( \exp( c n) \big)$ and $n \geq C$ for some constants $0<c<1$ and $C$. Define $\mathsf{range}_k = X_{k\pi_k(n)} - X_{k\pi_k(1)}$.

If $\lambda_n \geq 2 (8 \cdot 32) s \tilde{\sigma}  \sqrt{ \frac{1}{n} \log^2 np}$ then, with probability at least $ 1 - \frac{24}{n}$, for all $k \in S^c$, and for all $i'=1,...,n$
\begin{align*}
& \lambda_n > \mathsf{range}_k \Big| \frac{32}{n}\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)} \Big|  
\end{align*}
and $\max_{i'} \frac{X_{k\pi_k(i'+1)} - X_{k \pi_k(i')}}{\mathsf{range}_k} \leq \frac{1}{16}$ and $\mathsf{range}_k \geq 1$.

Therefore, for all $k \in S^c$, both the AC solution $\hat{f}_k$ from optimization~\ref{opt:alternate_opt}, and the DC solution $\hat{g}_k$ from optimization~\ref{opt:alternate_opt_concave} are zero. 
\end{theorem}

@@

Fix $j$ and $i$. Then $\hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}$ is the sum
of $n-i'+1$ random coordinates of $\hat{r}$. We will use
Serfling's theorem on the concentration of measure of sampling without
replacement (Corollary~\ref{cor:serfling}). We must first bound $\|
\hat{r} \|_\infty$ and $\frac{1}{n} \sum_{i=1}^n \hat{r}_i$ before we
can use Serfling's results however.

\vskip5pt
\textbf{Step 1}: {\it Bounding $\| \hat{r} \|_\infty$.} We have $\hat{r}_i = f_0(x_i) + w_i - \hat{f}(x_i)$ where
$\hat{f}(x_i) = \sum_{k \in S} \bar{\Delta}_k \hat{d}_k$ is the convex
additive function outputted by the restricted regression. Note that
both $f_0(x_i)$ and $\hat{f}(x_i)$ are bounded by $2sB$. 
Because $w_i$ is sub-Gaussian, $|w_i| \leq  \sigma \sqrt{2\log \frac{2}{\delta}}$ with probability at least $1-\delta$. By union bound across $i=1,...,n$, we have that $\| w\|_\infty \leq \sigma \sqrt{ 2 \log \frac{2n}{\delta}}$ with probability at least $1 - \delta$.

Putting these observations together,
%and take another union bound across all $j$ and all $i'$:
\begin{align}
\| \hat{r} \|_\infty &\leq 2sB + \sigma \sqrt{ 2\log \frac{2n}{\delta}}) \nonumber \\
      &\leq 4 s \tilde{\sigma} \sqrt{\log \frac{2n}{\delta}} \label{eqn:stepone_rhat}
\end{align}
with probability at least $1 - \delta$, where we have defined
$\tilde{\sigma} = \max(\sigma, B)$,
and assumed that $\sqrt{\log \frac{2np}{\delta}} \geq 1$. This assumption holds under the conditions in the theorem which state that $p \leq \exp( c n)$ and $n \geq C$ for some small constant $c$ and large constant $C$.

@@

\vskip5pt
\textbf{Step 3}: {\it Apply Serfling's theorem.}  
For any $k \in S^c$, Serfling's theorem states that with probability at least $1 - \delta$
\begin{align*}
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}\Big| \leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{2}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|
\end{align*}
We need Serfling's theorem to hold for all $k = 1,...,p$ and $i' =
1,...,n$. We also need the events that $\|\hat{r}\|_\infty$ and $|
\frac{1}{n} \hat{r}^\tran \mathbf{1}|$ are small to hold. Using a
union bound, with probability at least $1-\delta$, for all $k,i'$,
\begin{align*}
\Big
|\frac{1}{n} \hat{r}^\tran \mathbf{1}_{\pi_k(i':n)}\Big| &\leq
   2\| \hat{r} \|_\infty \sqrt{ \frac{1}{n} \log \frac{6np}{\delta}} + 
   \Big|\frac{1}{n} \hat{r}^\tran \mathbf{1} \Big|\\
  &\leq 4s\tilde{\sigma}\sqrt{\log \frac{6n}{\delta}} \sqrt{\frac{1}{n}\log \frac{6np}{\delta}} + 4 s \tilde{\sigma} \sqrt{\frac{1}{n}\log \frac{12}{\delta}} \\
  &\leq 8 s\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 \frac{12np}{\delta}}
\end{align*}
In the second inequality, we used equation~\eqref{eqn:stepone_rhat}
and equation~\eqref{eqn:steptwo_rhat} from steps 1 and 2
respectively. Setting $\delta = \frac{12}{n}$ gives the desired expression.

Finally, we note that $2 \geq (X_{k\pi_k(n)} - X_{k\pi_k(1)})$ since $X_k \subset [-1,1]$. This concludes the proof for the first part of the theorem.

To prove the second and the third claims, let the interval $[-1, 1]$ be divided into $64$ non-overlapping segments each of length $1/32$. Because $X_k$ is drawn from a density with a lower bound $c_l > 0$, the probability that every segment contains some samples $X_{ki}$'s is at least $1-64 \left( 1 - \frac{1}{32} c_l \right)^n$. Let $\mathcal{E}_k$ denote the event that every segment contains some samples.

Define $\mathsf{gap}_i = X_{k \pi_k(i+1)} - X_{k \pi_k(i)}$ for $i=1,...,n-1$ and define $\mathsf{gap}_0 = X_{k \pi_k(1)} - (-1)$ and $\mathsf{gap}_{n} = 1 - X_{k\pi_k(n)}$.

If any $\mathsf{gap}_i \geq \frac{1}{16}$, then $\mathsf{gap}_i$ has to contain one of the segments. Therefore, under event $\mathcal{E}_k$, it must be that $\mathsf{gap}_i \leq \frac{1}{16}$ for all $i$.

Thus, we have that $\mathsf{range}_k \geq 2 - 1/8 \geq 1$ and that for all $i$,

\[
\frac{X_{k\pi_k(i+1)} - X_{k \pi_k(i)}}{\mathsf{range}_k} \geq 
\frac{ 1/16 }{ 2 - 1/8} \geq 1/16
\]

Taking an union bound for each $k \in S^c$, the probability of that all $\mathcal{E}_k$ hold is at least $1 - p 64 \left( 1 - \frac{1}{32} c_l \right)^n$.

$p64 \left( 1 - \frac{1}{32} c_l \right)^n = 64 p \exp( - c' n)$ for some positive constants $0< c' < 1$ dependent on $c_l$. Therefore, if $p \leq exp( c n)$ for some $0<c < c'$ and if $n$ is larger than some constant $C$, $64 p \exp( - c' n) \leq 64 \exp( - (c' - c'') n) \leq \frac{12}{n}$.

Taking an union bound with the event that $\lambda_n$ upper bounds the partial sums of $\hat{r}$ and we establish the claim.

@@

\begin{theorem}
\label{thm:convex_consistent}
Let $\tilde{\sigma} \equiv \max(\sigma, B)$, and let $\hat{f}$ be the
minimizer of the restricted regression with $\lambda \leq 512 s
\tilde{\sigma} \sqrt{ \frac{1}{n} \log^2 np}$.
Suppose $n \geq c_1 s \sqrt{sB}$.
Then with probability at least $1-\frac{C}{n}$,
\begin{align}
\|f_0 - \hat{f} \|_P^2 - \| f_0 - f^* \|_P^2 
&\leq c B^2 \tilde{\sigma} \sqrt{ \frac{s^5}{n^{4/5}} \log^2 np},
\end{align}
where $c_1$ is an absolute constant and $c, C$ are constants possibly dependent on $b$.
\end{theorem}

@@

\begin{theorem}
\label{thm:concave_consistent}
Let $\hat{g}_k$ denote the minimizer of the concave postprocessing
step with $\lambda_n \leq 512 s\tilde{\sigma} \sqrt{\frac{1}{n} \log^2 np}$. Let $\tilde{\sigma} \equiv \max(\sigma, B)$.
Suppose $n$ is sufficiently large that $\frac{n^{4/5}}{\log^2 np} \geq c' B^4 \tilde{\sigma}^2 s^5$ where $c' \geq 1$ is a constant.
Then with probability at least $1- \frac{C}{n}$, for all $k=1,...,s$,
\[
\| f_0 - f^* - \hat{g}_k \|_P^2 - \| f_0 - f^* - g^*_k \|_P^2 \leq  c B^2 \tilde{\sigma}^{1/2} \sqrt[4]{ \frac{s^5}{n^{4/5}} \log^2 np}.
\]
\end{theorem}
